### 2019-05-28 doc/chapters/using_stainless.tex
Updated Bibiliography
fixed typos

To be verified the Scala code extended with Stainless annotations is passed to the framework as input.
The source code should be written in so called Pure Scala, a functional subset of Scala, so that Stainless can perform the verification.
Additionally the framework supports some imperative features. We will see some of this restrictions we have detected during this work in the next chapter.

\subsection{Functional Pure Scala}
The following functional elements are a part of Pure Scala:
\begin{itemize}
  \item \textbf{Algebraic Data Types:} abstract class, case class, case object. 
  The root of ADT is an abstarct class, unless only one case class or case object is defined.
  An abstract class cannot define fields and constructor arguments. 
  Case class and case object can extend an abstract class.
  An example of the ADT definition:
  \begin{lstlisting}[language=Scala]
    abstract class MyList
    case object MyEmpty extends MyList
    case class MyCons(elem: BigInt, rest: MyList) extends MyList
  \end{lstlisting}
  \item \textbf{Objects} for grouping classes and functions.
  An example of object definition:
  \begin{lstlisting}[language=Scala]
    object Specs {
      def increment(a: BigInt): BigInt = {
        a + 1
      }
    case class Identifier(id: BigInt)
    }
  \end{lstlisting}
  \item \textbf{Booleans:} logical operators  \textit{\&\&}, \textit{||}, \textit{!}, relational operator \textit{==}, Stainless syntax for boolean implication \textit{==>}. 
  The short-circuit interpretation is used, when the second argument of a boolean expression is evaluated only when needed.  
  \item \textbf{Generics.} Only invariant type parameters are supported, what means if S is subtype of T then List[S] and List[T] do not have sub-typing relationship.
  Covariant and contravariant type parameters, such as List[+T] and List[-T], are not supported. 
  Furthermore, only simple hierarchie is aloowed, when subclass must define the same type parameters in the same order as a parent class.
  An example using Generics:
  \begin{lstlisting}[language=Scala]
    object Test {
      abstract class List[T]
      case class Cons[T](hd: T, tl: List[T]) extends List[T]
      case class Nil[T]() extends List[T]
      def contains[T](l: List[T], el: T) = { ... }
    }
  \end{lstlisting}
  \item \textbf{Methods} can be defined in an abstract class and implemented or overridden in case classes. 
  The call of superclass methods with the keyword \textit{super} is allowed. 
  The method parameters can have default values. 
  An example of method definition in case of inheritance:
  \begin{lstlisting}[language=Scala]
    object Test {
      sealed abstract class Base {
        def double(x: BigInt): BigInt = x * 2
      }

      case class Override() extends Base {
        override def double(x: BigInt): BigInt = {
          super.double(x + 1) + 42
        }
      }
    }
  \end{lstlisting}
  \item \textbf{Pattern matching.} 
  Simple nested pattern matching, matching on type only, pattern quards and custom pattern matching with \textit{unapply} method are supported.
  \item \textbf{Values}. 
  Only immutable variables are allowed. Thus, they must be defined with the keyword \textit{val} (and not with \textit{var}).
  \item \textbf{Inner functions.}
  \item \textbf{Anonymous functions.}
  \item \textbf{Anonymous classes} with an explicit parent. 
  An anonymous class should have the same number of public members as its parent.
  An example of anonymous class implementation:
  \begin{lstlisting}[language=Scala]
    abstract class Foo {
      def bar: Int
    }

>>>>

To be verified the Scala code extended with Stainless annotations is passed to the framework as input.
The source code should be written in so called Pure Scala, a functional subset of Scala, so that Stainless can perform the verification.
Additionally, the framework supports some imperative features.
We will see some of these restrictions we have detected during this work in the next chapter.

\subsection{Functional Pure Scala}
The following functional elements are a part of Pure Scala:
\begin{itemize}
  \item \textbf{Algebraic Data Types:} abstract class, case class, case object. 
  The root of ADT is an abstract class, unless only one case class or case object is defined.
  An abstract class cannot define fields and constructor arguments. 
  Case class and case object can extend an abstract class.
  An example of the ADT definition:
  \begin{lstlisting}[language=Scala]
    abstract class MyList
    case object MyEmpty extends MyList
    case class MyCons(elem: BigInt, rest: MyList) extends MyList
  \end{lstlisting}
  \item \textbf{Objects} for grouping classes and functions.
  An example of object definition:
  \begin{lstlisting}[language=Scala]
    object Specs {
      def increment(a: BigInt): BigInt = {
        a + 1
      }
    case class Identifier(id: BigInt)
    }
  \end{lstlisting}
  \item \textbf{Booleans:} logical operators  \textit{\&\&}, \textit{||}, \textit{!}, relational operator \textit{==}, Stainless syntax for boolean implication \textit{==>}. 
  The short-circuit interpretation is used, when the second argument of a Boolean expression is evaluated only when needed.
  \item \textbf{Generics.} Only invariant type parameters are supported, what means if S is subtype of T then List[S] and List[T] do not have sub-typing relationship.
  Covariant and contravariant type parameters, such as List[+T] and List[-T], are not supported. 
  Furthermore, only simple hierarchies are allowed, when subclass must define the same type parameters in the same order as a parent class.
  An example using Generics:
  \begin{lstlisting}[language=Scala]
    object Test {
      abstract class List[T]
      case class Cons[T](hd: T, tl: List[T]) extends List[T]
      case class Nil[T]() extends List[T]
      def contains[T](l: List[T], el: T) = { ... }
    }
  \end{lstlisting}
  \item \textbf{Methods} can be defined in an abstract class and implemented or overridden in case classes. 
  The call of superclass methods with the keyword \textit{super} is allowed. 
  The method parameters can have default values. 
  An example of method definition in case of inheritance:
  \begin{lstlisting}[language=Scala]
    object Test {
      sealed abstract class Base {
        def double(x: BigInt): BigInt = x * 2
      }

      case class Override() extends Base {
        override def double(x: BigInt): BigInt = {
          super.double(x + 1) + 42
        }
      }
    }
  \end{lstlisting}
  \item \textbf{Pattern matching.} 
  Simple nested pattern matching, matching on type only, pattern guards and custom pattern matching with \textit{unapply} method are supported.
  \item \textbf{Values}. 
  Only immutable variables are allowed. Thus, they must be defined with the keyword \textit{val} (and not with \textit{var}).
  \item \textbf{Inner functions.}
  \item \textbf{Anonymous functions.}
  \item \textbf{Anonymous classes} with an explicit parent. 
  An anonymous class should have the same number of public members as its parent.
  An example of anonymous class implementation:
  \begin{lstlisting}[language=Scala]
    abstract class Foo {
      def bar: Int
    }
